### 2009-04-06 talk/icooolps2009-dotnet/paper.tex
fix an XXX
remove the fixed XXX

\anto{XXX: should we cite the DLR? How to prove that DLR programs are much
  slower than C\#?}
\davide{We can try writing something in the conclusion}

Recent developments show that JIT compilers can exploit runtime type
information to generate quite efficient code.  Unfortunately, writing a JIT
compiler is far from being simple.

>>>>

Recent developments show that \emph{Just In Time} (JIT) compilers can exploit runtime type
information to generate quite efficient code.  Unfortunately, writing a JIT
compiler is far from being simple.
